A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex
Editing background

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, human workforce. MTurk provides a simple interface for accessing human skill, allowing requesters to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs), which suggests that it was designed to accommodate tasks that are difficult for computers, but simple for people. This allows for research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}, as well as for large-scale annotation of training data for machine learning applications, including computer vision \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10} and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}. 
%In 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks \cite{callisonburch-dredze:2010:MTURK}.

Within MTurk, those who need work completed (`requesters') post individual `Human Intelligence Tasks,' or just `HITs'. A typical HIT  requires a few minutes of work and pays a few cents, although there is significant variation across HITs. Once a HIT is posted, MTurk workers (`Turkers') are free to choose to complete the HITs which interest them. Worker identities remain anonymous to requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards, and only pay workers from whom they accept tasks. 
Several reports examine Mechanical Turk as a marketplace \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that it has a diverse worker population that should represent a wide variety of languages.

>>>>

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, human workforce. MTurk provides a simple interface for accessing human skill, allowing requesters to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs), which suggests that it was designed to accommodate tasks that are difficult for computers, but simple for people. This allows for research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}, as well as for large-scale annotation of training data for machine learning applications, including computer vision \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10} and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}.

On MTurk researchers who need work completed are called `Requesters', workers are often referred to as `Turkers', and micro tasks are called `HITs'.  MTurk is a true market, meaning that Turkers are free to choose to complete the HITs which interest them, and Requesters can price their tasks competitively to try to attract workers and complete have their tasks done quickly \cite{faridani-et-al:2011,singer-mittal:2011}. Turkers' identities remain anonymous to Requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards.  Turkers are only pay if a Requester accepts their work.

Several reports examine Mechanical Turk as a marketplace \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that it has a diverse worker population that should represent a wide variety of languages.
